MSDS 7333 Case Study 06

### 2017-06-18 MSDS7333_CaseStudy06_MBaldree_BBrock_TElkins_AKelly.Rmd
Finished transcribing R-Markdown

>>>>

#### Average Signal Strength Distributions
To examine the distribution for all locations and angles of the two APs in question, we will generate the summary statistics. The summary statistics for all possible combinations of locations and orientations for each AP through the use of a new factor.

```{r}
offline$posXY = paste(offline$posX, offline$posY, sep="-")

# create data frames for each combination
byLocAngleAP = with(offline, by(offline, list(posXY, angle, mac), function(x) x))
```

Now, we calculate the summary statistics:
```{r}
signalSummary = lapply(byLocAngleAP, function(oneLoc) {
  ans = oneLoc[1, ]
  ans$medSignal = median(oneLoc$signal)
  ans$avgSignal = mean(oneLoc$signal)
  ans$num = length(oneLoc$signal)
  ans$sdSignal = sd(oneLoc$signal)
  ans$iqrSignal = IQR(oneLoc$signal)
  ans
})
offlineSummary = do.call("rbind", signalSummary)
```

The Standard Deviation of the average signal strength per targeted AP

```{r}
df = subset(offlineSummary, mac %in% c(chosenAP, rejectedAP), c(sdSignal, avgSignal, mac))
plotStdDevSignalStrength(df)
```

#### Let's dive into the K-Nearest Neighbors:
<font color = "red"><b>Discuss KNN here</b></font>

```{r}
macs = unique(offlineSummary$mac)
online = readData("online.final.trace.txt", subMacs = macs)
online$posXY = paste(online$posX, online$posY, sep = "-")
length(unique(online$posXY))
tabonlineXYA = table(online$posXY, online$angle)
#output shows measurements were taken at all angles throughout the floor
tabonlineXYA
```

Organize the data where each AP is in a column.

```{r}
onlineSummary = castOnline(online)
#confirm rejected AP is included
dim(onlineSummary)
names(onlineSummary)
```
